\documentclass[12pt,letterpaper]{article}
\usepackage{ifpdf}
\usepackage{mla}
\usepackage{outlines}
\begin{document}
\begin{mla}{Aron Fyodor M.}{Asor}{Mrs. Sandra Nicole Roldan}{En 12 - R40 / 090275}{\today}{.}

\input{parts/interviewdetails}

\subsection{Answers}
\begin{outline}[enumerate]
	\1  In case of abuse abroad,our brother Filipinos can take refuge of the criminal laws of the foreign country which is more or less similar to our own.  This is because the situs of the crime will determine the jurisdiction of the courts   thus, if the crime happens abroad it can only be tried therein.This is subject however to universal crimes such as genocide and terrorism which can be tried in another country other than where it is committed. 
		\2 It is my humble submission that our domestic laws cannot protect our OFWs if the crime is committed against them in another country.But if the abuse happens here, we have several laws that can be applied regardless of whether the victim is a Filipino or not.
		\2 In case of abuse committed abroad, our Government through the DFA has certain programs to assist the Filipino-victims.   
	\1 The definition of Rape is the latest revision made by our Congress taken into account the modern and prevailing situation. Thus, the previous understanding of rape as having carnal knowledge must give way to the existing definition. In this aspect, it is appropriate in the present time.
	\1  It is submitted that the current definition of rape can only be applied to female victims under the various ways enumerated under R.A. 8353. Under our Philippine laws, rape cannot be committed against male persons.
	\1 I'm sorry but I'm not aware of the Angara Bill so I cannot comment on that yet.
	\1 Since there can be no rape on male victims, the least he can use of is the crime of acts of lasciviousness under Article 336 of the Revised Penal Code. If there are injuries committed on him, he can also use the crime of physical injuries. And if he dies, homicide or murder as the case maybe.
	\1 Based on my understanding above-mentioned, these domestic laws cannot be applied if the crime is committed abroad. 
\end{outline}
\end{mla}
\end{document}
