Tentative thesis:\textit{ The Philippine Government is ignoring these Filipino male rape victims here and abroad by limiting anti-sexual abuse laws and support systems to their female counterparts.}



\begin{outline}[enumerate]
		\1 Introduction: Male rape is real and happening everywhere, everyday.
			\2 Current Male Rape facts and figures here in the Philippines and other countries.
			\2 The problems that male victims undergo, both mentally and socially:
				\3 The psychological trauma that the individual victim undergoes.
					\4 How such trauma is similar to the trauma that female rape victims undergo.
					\4 How such trauma is aggravated by lack of knowledge and misinformation on the part of the victim
					\4 How such trauma is aggravated by the male victim's peers.
				\3 Why male victims don't report to the police.
		\1 Analysis of the protection offered by the Philippines to male rape victims here and abroad.
			\2 Republic act 8353 also known as the Anti-rape law of 1997.
				\3 An analysis of the protection offered to male victims by the law.
				\3 Comparison to other foreign anti-rape laws, specifically the Sexual Offences (Scotland) Act of 2009.
			\2 The problems encountered by male rape victims seeking help from the Philippine Government.
				\3 Lack of hotlines and medical support.
				\3 Lack of training and preparedness by the police.
				\3 Lack of specific support groups and counseling for male rape survivors.
				\3 Lack of specific programs by the Department of Foreign Affairs for relieving and rescuing male rape victims abroad.
		\1 Conclusion: The Philippine Government has to acknowledge and protect Filipino male rape victims here and abroad.
			\2 A summary of the weak points in the legal and support system offered by the Philippines.
			\2 Recommendations to mitigate these weak points:
				\3 Broaden the current laws to accommodate male rape.
				\3 Set up an adequate support system for male rape victims.
					\4 Set up hotlines and male rape help desks.
					\4 Train both police officers and public hospitals in helping male survivors.
					\4 Set up programs to assist sexually abuse male OFWs abroad.
				\3 Increase the awareness of the general population regarding this type of rape.
\end{outline}
