\begin{workscited}

\bibent
Anti-rape law of 1997. Republic Act 8353. 30 Sept. 1997. Print.

\bibent
Cabahug, Boen. Email Interview. 21 Jan. 2010.
	
\bibent
Davies, Michelle, Paul Rogers and Jo-Anne Bates.``Blame towards male rape victims in a hypothetical sexual assault as a function of victim sexuality and degree of resistance.'' \textit{Journal of Homosexuality} 55.3 (2008): 533-544. Print.

\bibent
Ellis, Lee. Theories of Rape: \textit{Inquiries into the Causes of Sexual Aggression}. North Dakota: Hemisphere, 1989. Print.

\bibent
Graham, Ruth.``Male rape and the careful construction of the male victim.'' \textit{Social and Legal Issues} 15.2 (2006): 187-208. \textit{Academic Source Complete}. EBSCO. Web. 29 Jan. 2010.

\bibent
Groth, Nicholas and Ann Burgess.``Male rape: offenders and victims.'' \textit{American Journal of Psychiatry} 137.7 (1980): 806-810. Print.

\bibent
Jamel, Joanna and Ray Bull and Lorraine Sheridan.``An investigation of the specialist police service provided to male rape survivors.'' \textit{International Journal of Police Science and Management} 10.4 (2008): 486-508. Print.

\bibent
Philippines. National Statistics Office. \textit{Philippines in figures 2009}. NSO, 2009. Web. 4 Feb. 2010.

\bibent
Philippine Long Distance Telephone Company. \textit{PLDT Yellow Pages}. Kawit: PLDT, 2007. Print.

\bibent
Rape Victim and Protection Act of 1998. Republic Act 8505. 13 Feb. 1998. Print.

\bibent
Sable, Marjorie, et al.``Barriers to reporting sexual assault for women and men.'' \textit{Journal of American College Health} 55.3 (2006): 157-162. Print.

\bibent
Scarce, Michael.``Same sex rape of male college students.'' \textit{Journal of American College Health} 45.4 (1997): 171. \textit{Biomedical Reference Collection: Basic}. EBSCO. Web. 16 Jan. 2010.

\bibent
Schwartz, Martin and Walter DeKeseredy. \textit{Sexual Assault on the College Campus: The Role of Male Peer Support}. California: SAGE, 1997. Print.

\bibent
Sexual Offences (Scotland) Act 2009.14 July 2009. Print. 

\end{workscited}
